Time Series Modeling of Varying Complexity Captures Subdiffusive Solute Dynamics and Predicts Long Timescale Behavior in Nanoscale Pores.

### 2019-12-17 Ben_Manuscripts/stochastic_transport/Draft.tex
Speed improvements using a static empirical distribution

  We observe that in many cases, the distribution of solutes within the membrane
  evolves slowly with time. We defined the perceived equilibration time point 
  for each solute based on the time at which the number of solutes inside the
  pores and tails stabilized. Nonetheless, we observe evidence of non-stationary
  solute behavior after equilibration, on the $\mu$s timescale. In Table~\ref{table:stationarity},
  we compare the MSD of the solutes calculated using trajectory data from the 
  first and second halves of the equilibrated simulation time. Ethylene glycol 
  and methanol show considerable differences in their MSDs. Urea and acetic acid
  appear to demonstrate satisfactory stationarity on the 5 $\mu$s timescale. The
  shapes of their MSDs curves are also very similar (see Figure~\ref{S-fig:msd_comparison}
  of the Supporting Information).

@@

  %BJC4: need figures to support these claims.
  The non-stationary behavior of ethylene glycol and methanol present themselves
  in different ways. On average, methanol molecules in the tails appear to be 
  drifting further away from the pore center with time. Methanol's small size 
  significantly increases the volume of accessible structural space. Ethylene 
  glycol appears to experience an increased incidence of long trapping times. 
  These problems probably cannot be addressed without more simulation time or 
  additional solute trajectories.

@@

  The models are capable of reasonably predicting the MD MSD values of the second
  half of the solute trajectories based on parameters generated from the first half
  when the dwell time distributions are parameterized by a power law with an 
  exponential cut-off. At long timescales, the MSD of Urea is under-predicted 
  for both the 1 and 2 mode models with the same true of acetic acid on short 
  timescales. Without truncation of the power law distribution, the MD 
  MSDs are underestimated in all cases because dwell times on the order of the
  MD simulation length are sampled and incorporated into the simulated anomalous
  diffusion trajectories. Considering the longest observed dwell time among all
  solutes was 1.3 $\mu$s by ethylene glycol, we believe truncation is well-justified.
  Although in most cases, the predicted MSD curves overlap the 1-$\sigma$ confidence
  intervals of the MD MSD curves, they appear to lie systematically below the mean. 
  It is not clear whether this is a consistent feature of the AD model since we 
  only used 2 solutes for this analysis.

@@

  From a qualitative perspective, the models only have moderate success at predicting
  the shape of the MSD curves. Error in the MSD curvature can help explain some of
  the error in the predicted MSD magnitudes. The curves predicted for Urea with both 1 
  and 2 modes appear to have too much curvature, which causes it to under-predict the 
  MSD at long timescales, while those of acetic acid lack curvature, leading the
  AD model to under-predict the MSD at short timescales.

@@

  This analysis also suggests that working with only half of the data we collected
  ($\sim$2$\mu$s post-equilibration) is not always sufficient for extracting reliable
  parameter estimates. In most cases, the magnitude of the MSD predictions after a 
  500 ns time lag are within or close to within error of the MD MSDs (for sFBMcut and
  sFLMcut), but still appear to systematically under-predict the mean. We may be
  operating on the border of the minimum amount of data required to accurately 
  parameterize the AD model. Longer simulations and more independent trajectories may
  be necessary. Therefore, in the next section we will work with parameters fit to the
  full equilibrated portion of the solute trajectories, doubling the data.

@@

  After a 1000 ns time lag, for all solutes except acetic acid, the 1 and 2 mode 
  AD models do a fairly good job of predicting the magnitude of the MD 
  MSD curves when we use truncated power laws. In all but one case (two mode 
  ethylene glycol), MSD curves predicted by the sFLMcut model are higher than 
  those predicted by the sFBMcut model because of the heavy tails of the L\'evy 
  stable hop length distribution.

  Qualitatively, the curves with the highest final MSDs (ethylene glycol and 
  methanol) show more linear growth and their shapes are well captured by the
  sFLMcut and sFBMcut AD models. The MSD curve of urea bends slightly and 
  that of acetic acid has the most significant curvature. When the MD MSD 
  curves bend, the MSD curves predicted by the sFBMcut model tends to more 
  accurately portray their curvature since the sFLMcut model tends to become 
  linear faster.

  Acetic acid is a notable exception as no model accurately predicts its
  MSD or curvature. Both sFBMcut and sFLMcut significantly over-predict the final
  MSD while sFBM and sFLM significantly under-predict it. Once again, it 
  appears that the Hurst parameter may be over-estimated. However, the parameters
  of the hop and dwell distributions may be improved over those used to produce
  Figures~\ref{fig:1mode_msd_comparison_ACH_train_front} and
  \ref{fig:2mode_msd_comparison_ACH_train_front}. A lower value of $H$ would 
  increase the curvature and reduce the AD predicted MSD to values more consistent
  with acetic acid's MD MSD.

  Despite their deviations from the MD, the ranking of the magnitude of predicted
  MSDs remains the same as MD: ethylene glycol $\approx$ methanol $>$ urea $>$ acetic acid.
%  The discrepancies between MD and the predictions of the AD model may be resolved
%  by gathering longer and a greater quantity of solute trajectories
  Therefore, we can use the current parameters to understand solute dynamics.

@@

  Turning first to the parameters of the 1 mode model, we can begin to break down the
  trends in solute MSDs. The parameters belonging to ethylene glycol and methanol are
  relatively similar which is consistent with their similar MD MSDs. Methanol 
  tends to stay trapped for less time and takes larger hops but the most substantial
  difference is with respect to their Hurst parameters. In fact, methanol has the lowest
  $H$ of all the solutes studied. It is possible that we have underestimated $H$ since 
  it appears that our model consistently under-predicts the methanol MSD curve relative
  to other solutes. However, it remains plausible that methanol does have a low $H$ 
  value because it spends the majority of its time outside the pore region where collisions
  with tails are frequent. Urea has the third highest MSD that is primarily a consequence of
  more frequent and long dwell times, indicated by lower values of $\alpha_d$ and 
  $\lambda$. Urea's hop lengths ($\sigma$) and correlation ($H$) are comparable to ethylene
  glycol and methanol. Acetic acid has the smallest MSD among the solutes studied due 
  to longer periods of entrapment and shorter hops. Its trapping behavior is parameterized
  by an $\alpha_d$ value significantly lower than other solutes, but an intermediate 
  $\lambda$ value, suggesting it experiences many medium length periods of entrapment. 
  Its hops are smaller but are slightly compensated by a heavier tailed distribution 
  (lower $\alpha_h$) than the other solutes.

  We can use the 2 mode model to gain an even deeper understanding of solute behavior
  in the pore versus in the tails. It is clear that solutes are significantly slowed 
  while they are in the tail region (mode 2) where long dwell times are more probable
  (smaller $\alpha_d$) and hops are smaller (smaller $\sigma$). Interestingly, 
  $\alpha_h$ for urea and acetic acid in the tails is 1.50 meaning its hop distribution
  is heavy tailed relative to ethylene glycol and methanol whose $\alpha_h$ values are
  more consistent with a Gaussian distribution ($\alpha$=2). Acetic acid and urea are
  structurally similar molecules, both planar with two heavy atoms attached to a 
  carbonyl group. Their small size and rigid shape may allow them to occasionally slip
  through gaps in the tails. Meanwhile, methanol is small enough that it does not need
  to make larger jumps to escape traps.

  Overall, the AD model does a reasonable job of predicting solute MSDs and its 
  parameters can help us further understand solute dynamics. Hops appear to be well
  modeled as anticorrelated draws from Gaussian and L\'evy stable distributions. 
  The data strongly suggests that one must truncate the power law dwell time 
  distributions in order to obtain accurate MSD estimates. We can further understand
  solute dynamics by adding radially dependent parameter distributions as in the 
  2 mode model. A significant amount of solute trajectory data is necessary 
  in order to achieve good parameter estimates. The exact amount of data required 
  is dependent on the solute studied. Solutes which achieve higher MSDs
  in a given amount of time appear to be more accurately parameterized.

@@

  % BJC4: I moved this discussion up. It used to be after I presented the parameters
  Solute size and chemical functionality influence which states are visited most frequently.
  In Figure~\ref{fig:state_probabilities}, we plotted the probabilities of occupying
  a given state at any time. Urea and acetic acid spend slightly more than half 
  their time in the tails (56\% and 62\% of their time respectively) while ethylene
  glycol spends about 44\% of its time in the tails. Urea and acetic acid's compact
  and flat structure allows it to more easily partition into the tails while ethylene
  glycol prefers the pore region due to its two hydrophilic hydroxyl groups. Meanwhile
  methanol spends 91 \% of its time in the tails likely due to its small size.

@@

  To create an MSDDM for each solute, we determined the state sequence associated
  with each solute trajectory and then generated emission distributions of fluctuations
  within each state as well as transitions between states. There are not enough 
  consecutive observations of each type of transition with which to study their 
  individual correlation structures so we grouped all transition distributions
  into a single distribution and measured the correlation of the series of all 
  transitions. We lose information about individual types of transitions, however, 
  we believe this is unavoidable without at least an order of magnitude of additional data.

@@

  Most of a solute's MSD is a consequence of transitions between the 8 states
  in Table~\ref{table:states}. Motion while trapped in a state is highly 
  anti-correlated as indicated by their consistently low Hurst parameters.
  Perfectly anti-correlated motion ($H$=0) results in no contribution to the solute's
  MSD. There is a weak negative trend in the Hurst parameter values as the number
  of simultaneously influencing trapping mechanisms increases (Figure~\ref{fig:H_v_state}). 
  Surprisingly, state 5 $H$ values are low despite the solutes being subject to no
  trapping mechanisms. Highly anti-correlated behavior in the pores in the absence of
  any trapping mechanism is likely caused by collisions with monomer head groups 
  within the pore region. The Hurst parameters for transitional (T) emissions are 2-18 times higher 
  than emissions from trapped states. The value of $\alpha_h$ for transition 
  emissions is also relatively low giving higher probabilities to larger hops.

  As solutes are influenced by more trapping interactions simultaneously (i.e. hydrogen
  bonding \textit{and} associated with sodium versus just hydrogen bonding), the 
  width of the hop length distribution, $\sigma$, decreases while its L\'evy index,
  $\alpha_h$, increases. Treating the tail and pore regions independently, $\sigma$
  is largest and $\alpha_h$ is smallest when solutes are not hydrogen bonding or 
  associating with sodium (states 1 and 5). Solutes are free to move and take 
  occasionally large hops. The smallest $\sigma$ and highest $\alpha_h$ values are
  measured when solutes are hydrogen bonding and associating with sodium at the
  same time (states 4 and 8). Motion is restricted by multiple tethers which 
  maintains a relatively narrow distribution of hop lengths.

@@

  Using the parameters shown in Figure~\ref{fig:msddm_parameters}, we simulated 
  1000 MSDDM trajectory realizations as described in Section~\ref{method:MSMs}
  then calculated their MSDs. The MSDDM over-estimates solute MSDs by c.a. 250--650 \%
  (see Figure~\ref{fig:msddm_performance}).

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{URE_msddm.pdf}
  \caption{Urea}\label{fig:URE_msddm}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{GCL_msddm.pdf}
  \caption{Ethylene Glycol}\label{fig:GCL_msddm}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{MET_msddm.pdf}
  \caption{Methanol}\label{fig:MET_msddm}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{ACH_msddm.pdf}
  \caption{Acetic Acid}\label{fig:ACH_msddm}
  \end{subfigure}
  \caption{The MSD curves predicted by the MSDDM significantly over-predict the
  magnitude and misrepresent the curvature of those generated from MD simulations.
  We expect urea and acetic acid to show some curvature on these time scales.}\label{fig:msddm_performance}
  \end{figure}

  %It is clear that the predictive
  %abilities of the MSDDM are inadequate but it is still possible to salvage
  %key insights.

  The MSDDM overestimates solute MSDs because correlation is lost every time a
  state switch occurs. Although correlation exists within each sequence, there
  is no memory of the previous state or state transition that can be built into
  the first emission of the most recent state. This implies that the first 
  value in a state sequence is a random draw from the underlying emission 
  distribution. Frequent transitions between states lead to an abundance of 
  short dwell times. It is difficult to accurately correlate short sequences so
  we are almost simulating uncorrelated draws from the emission distribution.
  In Figure~\ref{fig:T_sensitivity}, we demonstrate this effect by varying the
  transition matrix and simulating a simple 2-state model with parameters similar
  to those in Table~\ref{table:msddm_params} (we tabulated the parameters used 
  in Table~\ref{S-table:msddm_params} of the Supporting Information). We modified
  the probability transition matrix, $T$, in order to control the probability of 
  self-transitions (the diagonal elements of $T$). Larger self-transition 
  probabilities lead to longer dwell times in each state. We set the off-diagonal
  elements of $T$ to be equal values that make the rows of $T$ sum to unity when
  combined with the self-transition probabilities. As we increase the 
  self-transition probability, $T_{ii}$, the simulated MSD decreases. Consequently,
  longer dwell times in each state allow us to more accurately simulate the
  negative correlation that we observe in MD.

  \begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{T_sensitivity.pdf}
  \caption{As we increase the self-transition probabilities ($T_{ii}$) of an MSDDM,
  the simulated MSD of the process decreases because the negative correlation structure
  of individual state sequences is simulated more accurately.}\label{fig:T_sensitivity}
  \end{figure}

  % MRS4: be more clear here what mechanistic insight it offers.
  % BJC4: added a couple sentences after thesis
  The MSDDM offers mechanistic insight but cannot be used for reliable predictions
  of solute MSDs. We can obtain a detailed picture of dynamics within each state in
  terms of the magnitude of their fluctuations and correlation with previous 
  motion. Unfortunately correlation between adjacent same-state sequences is lost
  with our model which causes the MSDs to be significantly over-predicted. The MSDDM
  may be suitable for processes with rarer transitions between states. If we can 
  further reduce the state-space of our models, it may have better predictive success,
  but we lose mechanistic detail.

>>>>

  We observe that in many cases, the distribution of solutes within the membrane
  evolves slowly with time. We defined the perceived equilibration time point 
  for each solute based on the time at which the number of solutes inside the
  pores and tails stabilized. Nonetheless, we observe evidence of non-stationary
  solute behavior after equilibration, on the $\mu$s timescale. In Table~\ref{table:stationarity},
  we compare the MSD of the solutes calculated using trajectory data from the 
  first and second halves of the equilibrated simulation time. Ethylene glycol 
  and methanol show considerable differences in their MSDs. Urea and acetic acid
  appear to demonstrate satisfactory stationarity. The shapes of their MSDs curves
  are also very similar (see Figure~\ref{S-fig:msd_comparison} of the Supporting
  Information).

@@

%  The non-stationary behavior of ethylene glycol and methanol present themselves
%  in different ways. On average, methanol molecules in the tails appear to be 
%  drifting further away from the pore center with time. Methanol's small size 
%  significantly increases the volume of accessible structural space. Ethylene 
%  glycol appears to experience an increased incidence of long trapping times. 
%  These problems probably cannot be addressed without more simulation time or 
%  additional solute trajectories.

@@

  The models are capable of reasonably predicting the MD MSD values of the second
  half of the solute trajectories based on parameters generated from the first half
  when the dwell time distributions are parameterized by a power law with an 
  exponential cut-off. At long timescales, the MSD of Urea is under-predicted 
  for both the 1 and 2 mode models with the same true of acetic acid on short 
  timescales. Without truncation of the power law distribution, the MD 
  MSDs are underestimated in all cases because dwell times on the order of the
  MD simulation length are sampled and incorporated into the simulated anomalous
  diffusion trajectories. Considering the longest observed dwell time among all
  solutes was 1.3 $\mu$s by ethylene glycol, we believe truncation is well-justified.
  %Although in most cases, the predicted MSD curves overlap the 1-$\sigma$ confidence
  %intervals of the MD MSD curves, they appear to lie systematically below the mean. 
  %It is not clear whether this is a consistent feature of the AD model since we 
  %only used 2 solutes for this analysis.

@@

  From a qualitative perspective, the models only have moderate success at predicting
  the shape of the MSD curves. Error in the MSD curvature can also help explain some of
  the error in the predicted MSD magnitudes. The curves predicted for Urea with both 1 
  and 2 modes appear to have too much curvature, which causes it to under-predict the 
  MSD at long timescales, while those of acetic acid lack curvature, leading the
  AD model to under-predict the MSD at short timescales.

@@

  This analysis also suggests that working with only half of the data we collected
  ($\sim$ 2 $\mu$s post-equilibration) is not always sufficient for extracting reliable
  parameter estimates. In most cases, the magnitude of the MSD predictions after a 
  500 ns time lag are within or close to within error of the MD MSDs (for sFBMcut and
  sFLMcut), but still appear to systematically under-predict the mean. We may be
  operating on the border of the minimum amount of data required to accurately 
  parameterize the AD model. Longer simulations and more independent trajectories may
  be necessary. Therefore, in the next section we will work with parameters fit to the
  full equilibrated portion of the solute trajectories, doubling the data.

@@

  After a 1000 ns time lag, the 1 and 2 mode AD models do a fairly good job of 
  predicting the magnitude of the MD MSD curves when we use truncated power
  laws to describe the dwell time distributions. In most cases, the sFBMcut
  and sFLMcut models give very similar results probably because their $\alpha_h$
  parameter values are relatively close to 2, meaning the hop length distribution
  is nearly Gaussian even when fit to a more general L\'evy distribution.

  The deviation between the 1 mode MSD predictions and MD are primarily due
  to differences in their curvature at long time lags. The shape and magnitude of the curves appears accurate 
  at short time lags, however, the curves tend to undershoot the MD MSD mean
  as the time lag increases. As discussed in the previous section, long time
  positional anti-correlation may not exist in the MD system which results 
  in a shift from sub-linear to linear MSD behavior. Acetic acid exemplifies
  this point. At first glance, acetic acid's predicted MSD (sFLMcut and sFBMcut)
  appear to match the curvature of MD quite well, but closer examination reveals
  that the MD MSD curve actually shifts from a sub-linear to a linear regime 
  around 500 ns.

  The 2 mode models shows considerably less curvature at large time lags than
  the 1 mode model because the implementation of the 2 mode model prevents long
  timescale correlation. The width of the hop distribution changes every time
  a switch between pores and tails occurs. We are unaware of an appropriate
  technique which can correlate hops that come from different hop distributions, 
  therefore every time a mode switch occurs, the correlation structure is 
  broken. Solutes which switch between modes the least show the greatest
  curvature. Methanol spends $> 90\%$ of its time in the tails, so mode transitions
  are relatively rare and the predicted MSD has curvature. This artificially
  solves the problem of long timescale correlation, however we do not recommend this
  as it has no theoretical basis.

  % In all but one case (two mode 
  % ethylene glycol), MSD curves predicted by the sFLMcut model are higher than 
  % those predicted by the sFBMcut model because of the heavy tails of the L\'evy 
  % stable hop length distribution.

%  Qualitatively, the curves with the highest final MSDs (ethylene glycol and 
%  methanol) show more linear growth and their shapes are well captured by the
%  sFLMcut and sFBMcut AD models. The MSD curve of urea bends slightly and 
%  that of acetic acid has the most significant curvature. When the MD MSD 
%  curves bend, the MSD curves predicted by the sFBMcut model tends to more 
%  accurately portray their curvature since the sFLMcut model tends to become 
%  linear faster.
%  
%  Acetic acid is a notable exception as no model accurately predicts its
%  MSD or curvature. Both sFBMcut and sFLMcut significantly over-predict the final
%  MSD while sFBM and sFLM significantly under-predict it. Once again, it 
%  appears that the Hurst parameter may be over-estimated. However, the parameters
%  of the hop and dwell distributions may be improved over those used to produce
%  Figures~\ref{fig:1mode_msd_comparison_ACH_train_front} and
%  \ref{fig:2mode_msd_comparison_ACH_train_front}. A lower value of $H$ would 
%  increase the curvature and reduce the AD predicted MSD to values more consistent
%  with acetic acid's MD MSD.

%  Despite their deviations from the MD, the ranking of the magnitude of predicted
%  MSDs remains the same as MD: ethylene glycol $\approx$ methanol $>$ urea $>$ acetic acid.
%%  The discrepancies between MD and the predictions of the AD model may be resolved
%%  by gathering longer and a greater quantity of solute trajectories
%  Therefore, we can use the current parameters to understand solute dynamics.

@@

  Turning first to the parameters of the 1 mode model, we can begin to break down the
  trends in solute MSDs. The parameters belonging to ethylene glycol and methanol are
  relatively similar which is consistent with their similar MD MSDs. Methanol 
  tends to stay trapped for less time and takes larger hops but the most substantial
  difference is with respect to their Hurst parameters. In fact, methanol has the lowest
  $H$ of all the solutes studied. It is possible that we have underestimated $H$ since 
  it appears that our model under-predicts the methanol MSD curve relative
  to other solutes. However, it remains plausible that methanol does have a low $H$ 
  value because it spends the majority of its time outside the pore region where collisions
  with tails are frequent. Urea has the third highest MSD which is primarily a consequence of
  more frequent and longer dwell times, indicated by lower values of $\alpha_d$ and 
  $\lambda$. Urea's hop lengths ($\sigma$) and correlation ($H$) are comparable to ethylene
  glycol and methanol. Acetic acid has the smallest MSD among the solutes studied due 
  to longer periods of entrapment and shorter hops. Its trapping behavior is parameterized
  by an $\alpha_d$ value significantly lower than other solutes, but an intermediate 
  $\lambda$ value, suggesting it experiences many medium length periods of entrapment. 
  Its hops are smaller but are slightly compensated by a heavier tailed distribution 
  (lower $\alpha_h$) than the other solutes.

  We can use the 2 mode model to gain an even deeper understanding of solute behavior
  in the pore versus in the tails. It is clear that solutes are significantly slowed 
  while they are in the tail region where long dwell times are more probable
  (smaller $\alpha_d$) and hops are smaller (smaller $\sigma$). Interestingly, 
  $\alpha_h$ for urea and acetic acid in the tails is 1.50 meaning its hop distribution
  is heavy tailed relative to ethylene glycol and methanol whose $\alpha_h$ values are
  more consistent with a Gaussian distribution ($\alpha$=2). Acetic acid and urea are
  structurally similar molecules, both planar with two heavy atoms attached to a 
  carbonyl group. Their small size and rigid shape may allow them to occasionally slip
  through gaps in the tails. Meanwhile, methanol is small enough that it does not need
  to make larger jumps to escape traps.

  Overall, the AD model does a reasonable job of predicting solute MSDs and its 
  parameters can help us further understand solute dynamics. Hops appear to be well
  modeled as anti-correlated draws from Gaussian and L\'evy stable distributions. 
  The data strongly suggests that one must truncate the power law dwell time 
  distributions in order to obtain accurate MSD estimates. We can further understand
  solute dynamics by adding radially dependent parameter distributions as in the 
  2 mode model. A significant amount of solute trajectory data is necessary 
  in order to achieve good parameter estimates. The exact amount of data required 
  is dependent on the solute studied.

  %Solutes which achieve higher MSDs
  %in a given amount of time appear to be more accurately parameterized.

@@

  % BJC4: I moved this discussion up. It used to be after I presented the parameters
  % BJC5: The pore/tail percentages could potentially go in the previous section, with
  % the two-mode model.
  Solute size and chemical functionality influence which states are visited most frequently.
  In Figure~\ref{fig:state_probabilities}, we plotted the probabilities of occupying
  a given state at any time. Urea and acetic acid spend slightly more than half 
  their time in the tails (56\% and 62\% of their time respectively) while ethylene
  glycol spends about 44\% of its time in the tails. Urea and acetic acid's compact
  and flat structure allows it to more easily partition into the tails while ethylene
  glycol prefers the pore region due to its two hydrophilic hydroxyl groups. Meanwhile
  methanol spends 91 \% of its time in the tails likely due to its small size.

@@

  To create an MSDDM for each solute, we determined the state sequence associated
  with each solute trajectory and then generated emission distributions of fluctuations
  within each state as well as transitions between states. There are not enough 
  consecutive observations of each type of transition with which to study their 
  individual correlation structures so we grouped all transition distributions
  into a single distribution and measured the correlation of the series of all 
  transitions. We lose information about individual types of transitions, however, 
  we believe this is unavoidable without at least an order of magnitude of additional data.
  In theory, one could parameterize separate transition distributions for those
  which occur in the tails versus in the pores, however this would lead to the same
  issues shown by the anomalous diffusion model.

@@

  Most of a solute's MSD is a consequence of transitions between the 8 states
  in Table~\ref{table:states}. Motion while trapped in a state is highly 
  anti-correlated as indicated by their consistently low Hurst parameters.
  Perfectly anti-correlated motion ($H$=0) results in no contribution to the solute's
  MSD. There is a weak negative trend in the Hurst parameter values as the number
  of simultaneously influencing trapping mechanisms increases (Figure~\ref{fig:H_v_state}). 
  Surprisingly, state 5 $H$ values are low despite the solutes being subject to no
  trapping mechanisms. Highly anti-correlated behavior in the pores in the absence of
  any trapping mechanism is likely caused by collisions with monomer head groups 
  within the pore region. The Hurst parameters for transitional (T) emissions are up to 
  18 times higher than emissions from trapped states. The value of $\alpha_h$ for 
  transition emissions is also relatively low giving higher probabilities to larger hops.

  As solutes are influenced by more trapping interactions simultaneously (i.e. hydrogen
  bonding \textit{and} associated with sodium versus just hydrogen bonding), the 
  width of the hop length distribution, $\sigma$, decreases while its L\'evy index,
  $\alpha_h$, increases. Treating states in the tail and pore regions independently, 
  $\sigma$ is largest and $\alpha_h$ is smallest when solutes are not hydrogen bonding
  or associating with sodium (states 1 and 5). Solutes are free to move and take 
  occasionally large hops. The smallest $\sigma$ and highest $\alpha_h$ values are
  measured when solutes are hydrogen bonding and associating with sodium at the
  same time (states 4 and 8). Motion is restricted by multiple tethers which 
  maintains a relatively narrow distribution of hop lengths.

@@

  In most cases, The MSDDM predicts the magnitude of the MD MSDs within their 
  1-$\sigma$ confidence intervals. Using the parameters shown in 
  Figure~\ref{fig:msddm_parameters}, we simulated 1000 MSDDM trajectory 
  realizations for each solute, as described in Section~\ref{method:MSMs},
  then calculated their MSDs (see Figure~\ref{fig:msddm_performance}). Methanol's
  MSD is over-predicted at short timescales while acetic acid's entire MSD 
  curve is severely over-predicted.

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{URE_msddm.pdf}
  \caption{Urea}\label{fig:URE_msddm}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{GCL_msddm.pdf}
  \caption{Ethylene Glycol}\label{fig:GCL_msddm}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{MET_msddm.pdf}
  \caption{Methanol}\label{fig:MET_msddm}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{ACH_msddm.pdf}
  \caption{Acetic Acid}\label{fig:ACH_msddm}
  \end{subfigure}
  \caption{In most cases, the magnitude of the MSD curves predicted by the 
  MSDDM agree well with those generated from MD simulations. The predicted MSD
  curves of urea and ethylene glycol lie within the 1-$\sigma$ confidence 
  intervals of MD for all time lags. Methanol under-predicts the MSD at small
  time lags and acetic acid grossly over-predicts the MSD at all time lags.
  Like the anomalous diffusion model, the MSDDM doesn't fully capture the 
  curvature of the MD MSD curves. }\label{fig:msddm_performance}
  \end{figure}

  The dynamics of urea, ethylene glycol and, to a lesser extent, methanol 
  appear to be well-captured by the MSDDM. One could argue that the curves
  of ethylene glycol and urea are statistically indistinguishable. However, 
  it's possible that they may diverge on longer timescales due to differences
  in their curvature. Similarly, methanol's MD MSD is nearly linear while 
  the MSDDM prediction is curving downward implying that it may underestimate
  the MSD on longer timescales.

  The predicted MSD of acetic acid is severely over-estimated most likely due
  to poor parameterization. Acetic acid has a transitional Hurst parameter 
  $\sigma$ values that are very similar to Urea. Consequently, the final 
  magnitude of acetic acid's MSD actually lies just within the lower bound
  of Urea's MD MSD 1-$\sigma$ confidence interval.

  The MSDDM suffers similar shortcomings to the AD model. First, curvature 
  on long timescales due to positional anti-correlation may result in 
  underestimates of the MSD at large time lags. As suggested earlier, truncating
  the positional autocorrelation function may help solve this issue. Second, 
  parameterization can be challenging.

  The MSDDM offers mechanistic insight and, in 3 out of 4 cases, gives reasonable
  predictions of solute MSDs. We can used the MSDDM to obtain a detailed picture of dynamics within
  each state in terms of the magnitude of their fluctuations and correlation with previous 
  motion.

%  Unfortunately correlation between adjacent same-state sequences is lost
%  with our model which causes the MSDs to be significantly over-predicted. The MSDDM
%  may be suitable for processes with rarer transitions between states. If we can 
%  further reduce the state-space of our models, it may have better predictive success,
%  but we lose mechanistic detail.

% BJC5: following not true
%  The MSDDM overestimates solute MSDs because correlation is lost every time a
%  state switch occurs. Although correlation exists within each sequence, there
%  is no memory of the previous state or state transition that can be built into
%  the first emission of the most recent state. This implies that the first 
%  value in a state sequence is a random draw from the underlying emission 
%  distribution. Frequent transitions between states lead to an abundance of 
%  short dwell times. It is difficult to accurately correlate short sequences so
%  we are almost simulating uncorrelated draws from the emission distribution.
%  In Figure~\ref{fig:T_sensitivity}, we demonstrate this effect by varying the
%  transition matrix and simulating a simple 2-state model with parameters similar
%  to those in Table~\ref{table:msddm_params} (we tabulated the parameters used 
%  in Table~\ref{S-table:msddm_params} of the Supporting Information). We modified
%  the probability transition matrix, $T$, in order to control the probability of 
%  self-transitions (the diagonal elements of $T$). Larger self-transition 
%  probabilities lead to longer dwell times in each state. We set the off-diagonal
%  elements of $T$ to be equal values that make the rows of $T$ sum to unity when
%  combined with the self-transition probabilities. As we increase the 
%  self-transition probability, $T_{ii}$, the simulated MSD decreases. Consequently,
%  longer dwell times in each state allow us to more accurately simulate the
%  negative correlation that we observe in MD.
%  
%  \begin{figure}
%  \centering
%  \includegraphics[width=0.5\textwidth]{T_sensitivity.pdf}
%  \caption{As we increase the self-transition probabilities ($T_{ii}$) of an MSDDM,
%  the simulated MSD of the process decreases because the negative correlation structure
%  of individual state sequences is simulated more accurately.}\label{fig:T_sensitivity}
%  \end{figure}
